### 2009-10-21 AffineLieAlgebras/InformalNotes/article.tex
First draft of the formula

\documentclass[a4paper,12pt]{article}
\usepackage[unicode,verbose]{hyperref}
\usepackage{amsmath,amssymb,amsthm} \usepackage{pb-diagram}
\usepackage{ucs}
%\usepackage[utf8x]{inputenc}
%\usepackage[russian]{babel}
\usepackage{cmap}
\usepackage[pdftex]{graphicx}
\pagestyle{plain}
\theoremstyle{definition} \newtheorem{Def}{Definition}
\begin{document}
Plan:

@@

The decomposition of the representation of the algebra to the representations of the subalgebra can be symbolically written using formal characters and projection operator:
\begin{equation}
  \label{eq:3}
  L_{\frak{g}\downarrow \frak{a}}^{\mu }=\bigoplus\limits_{\nu \in P_{\frak{a}%
    }^{+}}b_{\nu }^{\left( \mu \right) }L_{\frak{a}}^{\nu }\quad
  \Longrightarrow\quad
  \pi_{\mathfrak{a}}(ch L^{\mu}_{\mathfrak{g}})=\sum_{\nu\in P^{+}_{\mathfrak{a}}}b^{(\mu)}_{\nu} ch L^{\nu}_{\mathfrak{a}}
\end{equation}
Now using the Weyl-Kac formula for the character of the module
\begin{equation}
  \label{eq:2}
  ch L^{\mu}=\frac{\sum_{\omega\in W} \epsilon(\omega) e^{\omega(\mu+\rho)-\rho}}{\prod_{\alpha\in\Delta^{+}}(1-e^{-\alpha})^{mult(\alpha)}}
\end{equation}
we obtain the equality
\begin{equation}
  \label{eq:4}
  \frac{\sum_{\omega\in W} \epsilon(\omega) e^{\omega(\mu+\rho)-\rho}}{\prod_{\alpha\in\Delta^{+}}(1-e^{-\alpha})^{mult(\alpha)}} = 
  \sum_{\nu\in P^{+}_{\mathfrak{a}}}b^{(\mu)}_{\nu}
  \frac{\sum_{\omega\in W_{\mathfrak{a}}}\epsilon(\omega)e^{\omega(\nu+\rho_{\mathfrak{a}})-\rho_{\mathfrak{a}}}}{\prod_{\beta\in \Delta_{\mathfrak{a}}^{+}}(1-e^{-\beta})^{mult_{\mathfrak{a}}(\beta)}}
\end{equation}

@@

>>>>

\documentclass[a4paper,12pt]{article}
\usepackage[unicode,verbose]{hyperref}
\usepackage{amsmath,amssymb,amsthm} \usepackage{pb-diagram}
\usepackage{ucs}
%\usepackage[utf8x]{inputenc}
%\usepackage[russian]{babel}
\usepackage{cmap}
\usepackage[pdftex]{graphicx}
\pagestyle{plain}
\theoremstyle{definition} \newtheorem{Def}{Definition}
%\usepackage{verbatim} 
\newenvironment{comment}
{\par\noindent{\bf TODO}\\}
{\\\hfill$\scriptstyle\blacksquare$\par}

\begin{document}
Plan:

@@

The decomposition of the representation of the algebra to the representations of the subalgebra can be symbolically written using formal characters and projection operator:
\begin{equation}
  \label{eq:3}
  L_{\frak{g}\downarrow \frak{a}}^{\mu }=\bigoplus\limits_{\nu \in P_{\frak{a}%
    }^{+}}b_{\nu }^{\left( \mu \right) }L_{\frak{a}}^{\nu }\quad
  \Longrightarrow\quad
  \pi_{\mathfrak{a}}(ch L^{\mu}_{\mathfrak{g}})=\sum_{\nu\in P^{+}_{\mathfrak{a}}}b^{(\mu)}_{\nu} ch L^{\nu}_{\mathfrak{a}}
\end{equation}
Now using the Weyl-Kac formula for the character of the module
\begin{equation}
  \label{eq:2}
  ch L^{\mu}=\frac{\sum_{\omega\in W} \epsilon(\omega) e^{\omega(\mu+\rho)-\rho}}{\prod_{\alpha\in\Delta^{+}}(1-e^{-\alpha})^{mult(\alpha)}}
\end{equation}
we obtain the equality
\begin{equation}
  \label{eq:4}
  \pi_{\mathfrak{a}}\left(\frac{\sum_{\omega\in W} \epsilon(\omega) e^{\omega(\mu+\rho)-\rho}}{\prod_{\alpha\in\Delta^{+}}(1-e^{-\alpha})^{mult(\alpha)}}\right) = 
  \sum_{\nu\in P^{+}_{\mathfrak{a}}}b^{(\mu)}_{\nu}
  \frac{\sum_{\omega\in W_{\mathfrak{a}}}\epsilon(\omega)e^{\omega(\nu+\rho_{\mathfrak{a}})-\rho_{\mathfrak{a}}}}{\prod_{\beta\in \Delta_{\mathfrak{a}}^{+}}(1-e^{-\beta})^{mult_{\mathfrak{a}}(\beta)}}
\end{equation}

@@

\begin{comment}
  When such a subset does exist?  
\end{comment}

Now we can multiply the equation (\ref{eq:4}) by the term
\begin{equation}
  \label{eq:5}
  \pi_{\mathfrak{a}}\left(\prod_{\alpha\in \Delta^{+}\setminus \Delta_{\bot}}(1-e^{-\alpha})^{mult_{\mathfrak{g}}(\alpha)} \right)
\end{equation}
This term is non-zero.

Also we can see that 
\begin{equation}
  \label{eq:6}
  \pi_{\mathfrak{a}} (P) \pi_{\mathfrak{a}}(1-e^{-\alpha})=\pi_{\mathfrak{a}}\left(P\cdot (1-e^{-\alpha})\right)
\end{equation}
The equation (\ref{eq:4}) takes the form
\begin{multline}
  \label{eq:7}
  \pi_{\mathfrak{a}}\left(\frac{\sum_{\omega\in W} \epsilon(\omega) e^{\omega(\mu+\rho)-\rho}}{\prod_{\alpha\in\Delta_{\bot}}(1-e^{-\alpha})^{mult(\alpha)}}\right) = \\
  \pi_{\mathfrak{a}}\left(\prod_{\alpha\in \Delta^{+}\setminus \Delta_{\bot}}(1-e^{-\alpha})^{mult_{\mathfrak{g}}(\alpha)} \right)\sum_{\nu\in P^{+}_{\mathfrak{a}}}b^{(\mu)}_{\nu}
  \frac{\sum_{\omega\in W_{\mathfrak{a}}}\epsilon(\omega)e^{\omega(\nu+\rho_{\mathfrak{a}})-\rho_{\mathfrak{a}}}}{\prod_{\beta\in \Delta_{\mathfrak{a}}^{+}}(1-e^{-\beta})^{mult_{\mathfrak{a}}(\beta)}}
\end{multline}
The right-hand side of this equation can be reorganised as in the paper \cite{ilyin812pbc}. We introduce anomalous branching coefficients $k_{\lambda}$.
\begin{equation}
  \label{eq:10}
  \sum_{\nu \in P_{\frak{a}}}b_{\nu }^{\left( \mu \right) }\Psi _{\left( \frak{%
        a}\right) }^{\left( \nu \right) }=\sum_{\lambda \in P_{\frak{a}}}k_{\lambda
  }^{\left( \mu \right) }e^{\lambda } 
\end{equation}
Also we multiply the equation (\ref{eq:7}) by the denominator of the right-hand side and get
\begin{multline}
  \label{eq:12}
  \prod_{\beta\in \Delta_{\mathfrak{a}}^{+}}(1-e^{-\beta})^{mult_{\mathfrak{a}}(\beta)}  \pi_{\mathfrak{a}}\left(\frac{\sum_{\omega\in W} \epsilon(\omega) e^{\omega(\mu+\rho)-\rho}}{\prod_{\alpha\in\Delta_{\bot}}(1-e^{-\alpha})^{mult(\alpha)}}\right) = \\
  \pi_{\mathfrak{a}}\left(\prod_{\alpha\in \Delta^{+}\setminus \Delta_{\bot}}(1-e^{-\alpha})^{mult_{\mathfrak{g}}(\alpha)} \right)
\sum_{\lambda \in P_{\frak{a}}}k_{\lambda
}^{\left( \mu \right) }e^{\lambda } 
\end{multline}

Now we should notice that if the set $\Delta_{\bot}$ is non-empty than Weyl reflections which correspond to the positive roots of $\Delta_{\bot}$ generate a subgroup $W_{\bot}$ of Weyl group $W$.

\begin{comment}
  Prove it  
\end{comment}

Then we can reorganise the summation on the left-hand side of the equation (\ref{eq:12}) in the following way
\begin{multline}
  \label{eq:13}
   \prod_{\beta\in \Delta_{\mathfrak{a}}^{+}}(1-e^{-\beta})^{mult_{\mathfrak{a}}(\beta)}  \;\pi_{\mathfrak{a}}\left(\frac{\sum_{\omega\in W} \epsilon(\omega) e^{\omega(\mu+\rho)-\rho}}{\prod_{\alpha\in\Delta_{\bot}}(1-e^{-\alpha})^{mult(\alpha)}}\right) = \\
   \prod_{\beta\in \Delta_{\mathfrak{a}}^{+}}(1-e^{-\beta})^{mult_{\mathfrak{a}}(\beta)}  \;\pi_{\mathfrak{a}}\left(\sum_{\omega\in W/W_{\bot}} \epsilon(\omega) \frac{\sum_{\nu\in W_{\bot}}\epsilon(\nu) e^{\nu \cdot \omega(\mu+\rho)-\rho}}{\prod_{\alpha\in\Delta_{\bot}}(1-e^{-\alpha})^{mult(\alpha)}}\right) 
\end{multline}

Let's denote the subalgebra with the root space spanned over the set $\Delta_{\bot}$ by $\mathfrak{a}_{\bot}$.
\begin{comment}
  Shouldn't we prove that such a subalgebra exists and is tractable?
\end{comment}
Then we see that
\begin{multline}
  \label{eq:14}
  \sum_{\omega\in W/W_{\bot}} \epsilon(\omega) \frac{\sum_{\nu\in W_{\bot}}\epsilon(\nu) e^{\nu \cdot \omega(\mu+\rho)-\rho}}{\prod_{\alpha\in\Delta_{\bot}}(1-e^{-\alpha})^{mult(\alpha)}} =\\
  \sum_{\omega\in W/W_{\bot}} \epsilon(\omega) e^{-\rho} \frac{e^{\rho_{\mathfrak{a}_{\bot}} }\sum_{\nu\in W_{\bot}}\epsilon(\nu) e^{\nu \cdot (\omega(\mu+\rho)-\rho_{\mathfrak{a}_{\bot}}+\rho_{\mathfrak{a}_{\bot}})-\rho_{\mathfrak{a}_{\bot}}}}{\prod_{\alpha\in\Delta_{\bot}}(1-e^{-\alpha})^{mult(\alpha)}}=\\
  \sum_{\omega\in W/W_{\bot}} \epsilon(\omega) e^{\rho_{\mathfrak{a}_{\bot}}-\rho} ch L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}
\end{multline}
The projection $\pi_{\mathfrak{a}}$ of the character of the highest-weight module $L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}$ is equal to the dimension of the module multiplied by $e^{\pi_{\mathfrak{a}}(\omega(\mu+\rho)-\rho_{\mathfrak{a}_{\bot}})}$
  \begin{multline}
    \label{eq:15}
    \pi_{\mathfrak{a}}\left(\sum_{\omega\in W/W_{\bot}} \epsilon(\omega) e^{\rho_{\mathfrak{a}_{\bot}}-\rho} ch L^{\omega(\mu+\rho)-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}\right) = \\
    \sum_{\omega\in W/W_{\bot}} \epsilon(\omega) dim\left(L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}\right) e^{\pi_{\mathfrak{a}}(\omega(\mu+\rho)-\rho)}
  \end{multline}
These dimensions of the modules could be easily calculated using Weyl formula.
